 Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation

### 2021-06-03 analysis/paper/shceof.Rmd
Mejora la descripción del método cEOF
Closes  #45

Complex Empirical Orthogonal Functions (cEOF) is a useful method to characterise zonal waves, considering phase-varying structures [@horel1984].
This method involves augmenting \textcolor{red}{No sé si es un vocabulario específico de usar este método, pero no me queda claro que se entiende por "augmenting" exactamente} the original fields with the Hilbert transform of the data and then computing the Singular Value Decomposition of it.
In this work, instead of applying the Hilbert transform to the time series at each point, we apply it to each latitude circle at each moment in time \textcolor{red}{Esta aclaración la haces por qué es la manera usual de hacer la metodología, si es asi aclaralo.}.
Since each latitude circle is a periodic domain, this procedure does not suffer from edge effects.
The result of the cEOF methodology is a set of complex spatial patterns and complex time series.
The real and imaginary part of each spatial pattern represent two phases wave-like spatial patterns that are in quadrature.
The magnitude and argument of each complex time series represent the amplitude and phase of each zonal wave.

>>>>

Complex Empirical Orthogonal Functions (cEOF) is a useful method to characterise zonal waves, considering phase-varying structures [@horel1984]. 
This method involves computing EOF on the analytic representation of the original field. 
This representation is a complex field in which the real part is the original variable and the imaginary part is the original data shifted by 90\degree at each spectral frequency -- i.e. its Hilbert transform. 
The Hilbert transform is usually understood in terms of time-varying signal. 
However, in this work we apply the Hilbert transform to each latitude circle at each moment in time.
Since each latitude circle is a periodic domain, this procedure does not suffer from edge effects.

The result of the cEOF methodology is a set of complex spatial patterns and complex time series.
The real and imaginary part of each spatial pattern represent two phases wave-like spatial patterns that are in quadrature.
The magnitude and argument of each complex time series represent the amplitude and phase of each zonal wave.
